Finance and Income Inequality - panel BMA approach\thanks{We thank two anonymous referees, ...}

### 2019-12-03 Paper/paper.tex
update 191203

\documentclass[a4paper,11pt]{article}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb} %better typesetting of mathematical expressions, theorems, additional symbols
\usepackage{booktabs} %fixltx2e
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
% \usepackage[capposition=top]{floatrow}
\usepackage{caption}
\captionsetup[measuredfigure]{labelformat=empty}
% \usepackage{bm}
% \usepackage{subcaption}
%\usepackage{epstopdf} % not supported by xelatex
% \usepackage{fullpage}
% \usepackage{enumerate}
\usepackage{authblk}
\usepackage{fontspec}
\usepackage{lscape}
\usepackage[round]{natbib} %standard package for bibliography
\usepackage{multirow}
% \usepackage[figuresleft]{rotating}
\usepackage[dvipsnames]{xcolor}
\usepackage{colortbl} % color table
\usepackage{geometry}
% \usepackage{hyperref} %hyperlink support
% \hypersetup{pdfstartview={XYZ null null 1.00},bookmarksnumbered, hypertexnames=false, colorlinks=true, linkcolor=BrickRed, citecolor=MidnightBlue, urlcolor=MidnightBlue} % zoom: default screen; numbers for bookmarks

@@

\citet{marrero2013inequality} introduce two types of inequality - inequality of oppportunity and inequality of effort/luck. Applying this to the EU countries and US states, they show that inequality of opportunity (driven by race, parental education, citizenship, ...) is negatively related to growth while the residual "good" inequality is growth inducing.

\section{Data}
% \label{sec:data}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb} %better typesetting of mathematical expressions, theorems, additional symbols
\usepackage{booktabs} %fixltx2e
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
% \usepackage[capposition=top]{floatrow}
\usepackage{caption}
% \captionsetup[measuredfigure]{labelformat=empty}
% \usepackage{bm}
% \usepackage{subcaption}
%\usepackage{epstopdf} % not supported by xelatex
% \usepackage{fullpage}
% \usepackage{enumerate}
\usepackage{authblk}
\usepackage{fontspec}
\usepackage{lscape}
\usepackage[round]{natbib} %standard package for bibliography
\usepackage{multirow}
% \usepackage[figuresleft]{rotating}
\usepackage[dvipsnames]{xcolor}
\usepackage{colortbl} % color table
\usepackage{geometry}
% \usepackage{hyperref} %hyperlink support
% \hypersetup{pdfstartview={XYZ null null 1.00},bookmarksnumbered, hypertexnames=false, colorlinks=true, linkcolor=BrickRed, citecolor=MidnightBlue, urlcolor=MidnightBlue} % zoom: default screen; numbers for bookmarks

@@

\citet{marrero2013inequality} introduce two types of inequality - inequality of oppportunity and inequality of effort/luck. Applying this to the EU countries and US states, they show that inequality of opportunity (driven by race and parental education ...) is negatively related to growth while the residual "good" inequality is growth inducing.

Income inequality and growth may intersect through varying channels. Accumulation of savings, unobservable effort, and investment project size favour the prediction on growth inducing inequality. Negative impact of inequality on human capital accumulation, entrepreneurial activity, and hence growth provides argument for the opposing view.
\section{Data}
% \label{sec:data}
